Steve Linberg

### 2022-02-25 steve.Rmd
update photo

---
title: "Steve Linberg"
image: "2021-sfl-photo-fadedbg-256.png"
links:
  - label: LinkedIn
    url: "https://www.linkedin.com/in/slinberg"
  - label: Twitter
    url: "https://twitter.com/stevelinberg"
  - label: GitHub
    url: "https://github.com/stevelinberg"
  - label: SO
    url: "https://stackoverflow.com/users/13603796/stevelinberg"
  - label: Email
    url: "mailto:steve@slinberg.net"
output:
  postcards::trestles
---

>>>>

---
title: "Steve Linberg"
image: "2022-sfl-photo-400x400.jpg"
links:
  - label: LinkedIn
    url: "https://www.linkedin.com/in/slinberg"
  - label: Twitter
    url: "https://twitter.com/stevelinberg"
  - label: GitHub
    url: "https://github.com/stevelinberg"
  - label: SO
    url: "https://stackoverflow.com/users/13603796/stevelinberg"
  - label: Email
    url: "mailto:steve@slinberg.net"
output:
  postcards::trestles
---
